\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{Paper Précis: Creating a Shared Understanding of Testing Culture on a Social Coding Site}

### 2014-11-23 article_2.tex
Final (edited)

\vspace{1mm}
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
\noindent 
Software engineering is inherently collaborative, at the team, project and community levels. However many project
owners battle with establishing and communicating a testing culture that is appropriate for their project's needs.
Transparent software environments such as Github incorporate social media features to make work more visible. 
Previous research forwards that this transparency influences the behaviour of developers. Our basing paper
extends upon those findings to investigate how the increased transparency found on GitHub influences testing 
behaviours.\par
From interviewing active GitHub users, both project owners and developers, our basing paper 
suggests several strategies that software teams can use to positively influence the testing behaviour in their projects. Additionally, it is found that project owners on GitHub are often not aware of these strategies. This research reports on the difficulties and risks which this causes and suggests guidelines for developing a sustainable testing culture.

@@

For the initial data collection phase a survey was designed which included five questions to better help "understand how testing practices evolve based on the interaction between contributors and project owners on social coding sites" \citep{Pham}. This questionnaire (Q1) analysed the following topics:
\begin{itemize}
	\item how project owners assess incoming contributions
	\item internal and external motivations for engaging in testing efforts
	\item the challenges and risks related to testing
	\item how developers code with those challenges and risks
	\item	the impact of participating on social coding projects has on testing practices
\end{itemize}

@@

Grounded Theory involves continuous data collection accompanied with periodic pauses for analysis. Accordingly, our basing study was conducted in three incremental phases of analysis. Pham first enlisted a diverse sample population though inviting active GitHub users belonging to popular OSS projects and random recently active users. The first phase sought to understand which testing-related norms and conventions exist on Github through asking participants to outline their testing process in one of their public projects. The findings here reflected that projects featuring extensive collaboration between developers demanded more elaborate testing approaches. They also indicated that most decisions regarding testing were made when PRs were sent and received, hence when people had to coordinate and negotiate their cooperation.
\par
Subsequently, the second phase of the analysis involved refining the target population to be "active users who used the collaboration features of GitHub" \citep{Pham}. Such was achieved by inviting the sample pool to take the first questionnaire (Q1), whereby the questionnaire responses made it possible to distinguish those users that had been collaboratively active and their approaches for testing. The refined target population were then invited to a round of semi-structured interviews exploring participant's testing practices and values. Several common themes emerged from these interviews:
\begin{enumerate}
	\item The social network features, fork and PR mechanisms, and integration of numerous tools result 		in a GitHub-specific process for sending and receiving contributions.
	\item GitHub tools and social features lower the barriers for engagement in software projects.
	\item GitHub integrates many tools into the project context and centralises many interactions and notifications among participants.
	\item GitHub provides increased social transparency that allows its users to see the identity, actions, and communications between users
\end{enumerate}
In the last phase, a final questionnaire (Q2) was sent to random GitHub users for quantitative validation of Pham's findings, this is outlined in section V.

@@

\par
\textbf{\textit{Motivations for Demanding \& Delivering Tests:}} Owners had varied reasons for requiring tested contributions. According to one owner, maintaining clean and well documented code reduced the subsequent support effort. Some owners considered tests as a form of documentation of how to use the contributed feature. In another case, owners required acceptance-style tests to in turn communicate requirements. \par
In interviews with contributors, different motivations emerged for including tests in a PR. Some felt that explicitly adding tests highlighted the value of their contribution to the owner. Contributors identified existing tests in a project as informal project guidelines; thus feeling obligated to add their own tests. This obligation also appears from customs rooted in the community of the technology used. Ruby developers tested their contribution by default.

\textbf{\textit{Challenges and Risks:}} Interviewees saw an urgent need for automatic tests in their projects. They reported that many types of contributions needed to be managed and for reasons of scale could not be done using manual tests. In achieving automated testing, owners often saw it mandatory that a PR was to include respective tests. \citet{Pham} also discovered that projects who fail to "communicate testing culture efficiently and effectively", or who "set barriers that are too high for first-time contributors", will struggle to create and maintain a testing culture. For instance, if new contributors cannot easily find existing tests in a project, they will not be able to write any of their own. 
\par
Many owners expressed that their projects were struggling with creating the required testing culture, PRs received would often not include any tests by default. One issue they saw was the voluntary nature of OSS contributions: they could not simply require well-tested contributions.

@@

\textbf{\textit{Impact of Social Coding Sites on Testing Practices:}} \citet{Pham} encountered different levels of lowering the effort for testing. One interviewee suggested that projects which use behaviour driven development (BDD) and concentrated on testing primarily the main use cases provided these low barriers to entry. A more extreme case of lowering the barrier for contributions was to defer testing to a later point. 
\par
Interviewees told us that effectively communicating a project's testing culture would lead to contributors adopting that culture more rapidly and in greater numbers. According some, better communication of testing culture leads to more PRs containing tests. Providing guidelines on contributing or dedicated testing tutorials removed uncertainties in contributors about how to participate correctly. Projects not communicating a testing culture often received PRs with no tests. 
\par
Central to owners creating and nurturing a testing culture is to supply existing tests and a simple testing infrastructure. Contributors reported this to lower the barrier, in turn increasing confidence in the correctness of their own code. Interviewees also argued that just having a test suite communicates certain values regarding testing, helping them understand the project's testing culture, norms, and conventions. 
\par
Since moving their projects to GitHub, interviewees reported that the number of volunteer contributions increased. They attributed this to the low barriers to entry and the resulting exposure to a larger number of developers. Many claimed that the public nature of GitHub results in improvements around testing practices. Some of these were "companies that used the exemplary testing practices in their public projects as an advertisement for the high quality of their development services". Similar was found in OSS projects, core members were concerned about the project's reputation and believed proper testing would lead to higher quality code, which in turn would be received better by others. One interviewee reported that having contributed to a high-profile project where tests are mandatory would help him find work.

>>>>

\vspace{1mm}
\renewcommand{\abstractname}{Abstract}
\begin{abstract}
\noindent 
Software engineering is inherently collaborative, at the team, project and community levels. However many project
owners battle with establishing and communicating a testing culture that is appropriate for their project's needs.
Transparent software environments such as Github incorporate social media features to make work more visible. 
Previous research forwards that this transparency influences the behaviour of developers. Our basing paper
extends upon those findings to investigate how the increased transparency found on GitHub influences testing 
behaviours.\par
From interviewing active GitHub users, both project owners and developers, our basing paper 
suggests several strategies that software teams can use to positively influence the testing behaviour in their projects. Additionally, it is found that project owners on GitHub are often not aware of these strategies. This research reports on the difficulties and risks this causes and suggests guidelines for developing a sustainable testing culture.

@@

For the initial data collection phase a survey was designed which included five questions to better help "understand how testing practices evolve based on the interaction between contributors and project owners on social coding sites" \citep{Pham}. This questionnaire (Q1) analysed the following topics:
\begin{itemize}
	\item how project owners assess incoming contributions
	\item internal and external motivations for engaging in testing efforts
	\item the challenges and risks related to testing
	\item how developers code with those challenges and risks
	\item	the impact of participating on social coding projects on testing practices
\end{itemize}

@@

Grounded Theory involves continuous data collection accompanied with periodic pauses for analysis. Accordingly, our basing study was conducted in three incremental phases of analysis. Pham first enlisted a diverse sample population though inviting active GitHub users belonging to popular OSS projects and random recently active users. The first phase sought to understand which testing-related norms and conventions exist on GitHub through asking participants to outline their testing process in one of their public projects. The findings here reflected that projects featuring extensive collaboration between developers demanded more elaborate testing approaches. They also indicated that most decisions regarding testing were made when PRs were sent and received, hence when people had to coordinate and negotiate their cooperation.
\par
Subsequently, the second phase of the analysis involved refining the target population to be "active users who used the collaboration features of GitHub" \citep{Pham}. Such was achieved by inviting the sample pool to take the first questionnaire (Q1), whereby the questionnaire responses made it possible to distinguish those users that had been collaboratively active and their approaches for testing. The refined target population were then invited to a round of semi-structured interviews exploring participant's testing practices and values. Several common themes emerged from these interviews:
\begin{enumerate}
	\item The social network features, fork and PR mechanisms, and integration of numerous tools result 		in a GitHub-specific process for sending and receiving contributions.
	\item GitHub tools and social features lower the barriers for engagement in software projects.
	\item GitHub integrates many tools into the project context and centralises many interactions and notifications among participants.
	\item GitHub provides increased social transparency that allows its users to see the identity, actions, and communications between users
\end{enumerate}
In the last phase, a final questionnaire (Q2) was sent to random GitHub users for quantitative validation of Pham's findings, this is outlined in section V.

@@

\textbf{\textit{Motivations for Demanding \& Delivering Tests:}} Owners had varied reasons for requiring tested contributions. According to one owner, maintaining clean and well documented code reduced the subsequent support effort. Some considered tests as a form of documentation of how to use the contributed feature. In another case, owners required acceptance-style tests to in turn communicate requirements. \par
In contributor interviews, different motivations emerged for including tests in a PR. Some felt that explicitly adding tests highlighted the value of their contribution to the owner. Contributors identified existing tests in a project as informal project guidelines; thus feeling obligated to add their own tests. This obligation also appears from customs rooted in the community of the technology used. Ruby developers tested their contribution by default.
\par
\textbf{\textit{Challenges and Risks:}} Interviewees saw an urgent need for automatic tests in their projects. They reported that many types of contributions needed to be managed and for reasons of scale could not be done using manual tests. In achieving automated testing, owners often saw it mandatory that a PR was to include respective tests. It was also discovered that projects who fail to "communicate testing culture efficiently and effectively", or who "set barriers that are too high for first-time contributors", will struggle to create a testing culture. For instance, if new contributors cannot easily find existing tests in a project, they will not be able to write any of their own. 
\par Many felt that their projects were struggling with creating the required testing culture, PRs received would often not include any tests by default. One issue they saw was the voluntary nature of OSS contributions: they could not simply require well-tested contributions.

@@

\textbf{\textit{Impact of Social Coding Sites on Testing Practices:}} \citet{Pham} encountered different levels of lowering the effort for testing. One interviewee suggested that projects which use behaviour driven development (BDD) and concentrated on testing primarily the main use cases provided these low barriers to entry. A more extreme case of lowering the barrier for contributions was to defer testing to a later point. 
\par
Interviewees told us that effectively communicating a project's testing culture would lead to contributors adopting that culture more rapidly and in greater numbers. According to some, a better communication of testing culture leads to more PRs containing tests. Providing guidelines on contributing or dedicated testing tutorials removed uncertainties in contributors about how to participate correctly. Projects not communicating a testing culture often received PRs with no tests. 
\par
Central to owners creating and nurturing a testing culture is to supply existing tests and a simple testing infrastructure. Contributors reported this to lower the barrier, in turn increasing confidence in the correctness of their own code. Interviewees also argued that just having a test suite communicates certain values regarding testing, helping them understand the project's testing culture, norms, and conventions. 
\par
Since moving their projects to GitHub, interviewees reported that the number of volunteer contributions increased. They attributed this to the low barriers to entry and the resulting exposure to a larger number of developers. Many claimed that the public nature of GitHub results in improvements around testing practices. Some of these were "companies that used the exemplary testing practices in their public projects as an advertisement for the high quality of their development services". Similar was found in OSS projects, core members were concerned about the project's reputation and believed proper testing would lead to higher quality code, which in turn would be received better by others. One interviewee reported that having contributed to a high-profile project where tests are mandatory would help him find work.
